---
title: "Wk Edits"
author: "Warrenkevin Henderson"
date: "11/17/2021"
output: html_document
---

---
title: "Zalbert_OriginalHomeworkCode_05"
author: "Zoe Albert"
date: "11/11/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
###Using bootstrapping, we could also do the same for estimating standard errors and CIs around regression parameters, such as β coefficients.

###[1] Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).

library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
summary(d)
###First things first, I need to load 

library(lmodel2)
###I have to download this in order 

homerange <- log(d$HomeRange_km2)
###Log is a built in function
###I use the dollar sign to get out a certain point. 

bodymass <- log(d$Brain_Size_Female_Mean)
###I do the log again but this time for bodymass. 

c <- cbind(d, homerange, bodymass)
###I want to do these together, so now I am going to use cbind.
###I am not sure if there is a specific way to space these. 
###Do I need to name this? I am not sure if I need to do x<-...I think I need to for the formula, so I just named it c. 

l <- lmodel2(homerange~bodymass, data= c  , range.y ="interval" , range.x="relative"  , nperm=0)
###Now I want to use the actual function that I called earlier. 
###I don't know what to make range.x and range.y, but this is what r seems to want me to do.
###Zero idea what nperm is and how to determine

mx <- l$regression.results$slope
###I want to get slope from regression 
###I get green, but I don't know where to find the slope

b <-l$regression.results$Intercept
###Intercept 
```
###[2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.
 
###Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.
```{r}
s1 <- NULL
s2 <- NULL
for (i in 1:1000) { s1[[i]] <- sample(d$HomeRange_km2, size =100, replace=TRUE)
s2[[i]] <- sample(d$Body_mass_female_mean, size = 100, replace=TRUE)}
# I re-ran your code and it worked. Try putting it on a new line??

mm <- NULL
for (i in 1:1000) {
  mm[[i]] <- lmodel2(s1[[i]]~s2[[i]],data = f, range.y = "interval", range.x = "relative")
beta1[i] <-mm[[i]]$regression.results$Slope[1]
beta0[i] <-mm[[i]]$regression.results$Intercept[1]
}
###This isn't working because my last one didn't work, I think?

###How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?
###Waiting until I can figure out my problem before I can answer this?

###How does the latter compare to the 95% CI estimated from your entire dataset?
###I again feel like I have to wait, but its sd. Right?
```

###Come back to extra credit with help of group
###Issues during this homework:
1) I want to find a better way to display the slope and intercept. 
2)As soon as my first formula was messed up on my second one I could not figure out where to go from there.
3) How do I know what to put into the formulas as values???
4)
5)